#Libraries required
rm(list=ls())     
```

1. Load data, clean data
```{r}
library(data.table)
library(lfe)
library(stargazer)
library(gdata)
library(ggplot2)
library(psych) 
library(ggeffects)
library(QuantPsyc)
library(VIF)
library(usdm)
library(lmtest)
library(multiwayvcov)
library(sandwich)
library(foreign)

df = fread("JUNO FB Ads-Jul-1-2018-Feb-28-2019.csv")

colnames(df)[colnames(df)=="Campaign Name"] <- "campaign_name"
colnames(df)[colnames(df)=="Campaign ID"] <- "campaign_ID"
colnames(df)[colnames(df)=="Result Type"] <- "result_type"
colnames(df)[colnames(df)=="Results [On Ad]"] <- "results_on_ad"

colnames(df)[colnames(df)=="Result Rate"] <- "result_rate"
colnames(df)[colnames(df)=="Result Rate [On Ad]"] <- "result_rate_on_ad"
colnames(df)[colnames(df)=="Cost per Result"] <- "cost_per_result"
colnames(df)[colnames(df)=="Cost per Result [On Ad]"] <- "cost_per_result_on_ad"

colnames(df)[colnames(df)=="Amount Spent (USD)"] <- "amount_spent_USD"
colnames(df)[colnames(df)=="CPM (Cost per 1,000 Impressions)"] <- "CPM"
colnames(df)[colnames(df)=="Cost per 1,000 People Reached"] <- "CPPR"
colnames(df)[colnames(df)=="Link Clicks"] <- "link_clicks"

colnames(df)[colnames(df)=="Link Clicks [On Ad]"] <- "link_clicks_on_ad"
colnames(df)[colnames(df)=="Clicks (All)"] <- "clicks_all"
colnames(df)[colnames(df)=="CPC (All)"] <- "CPC_all"
colnames(df)[colnames(df)=="CPC (Cost per Link Click)"] <- "CPC_per_link"

colnames(df)[colnames(df)=="CPC (Cost per Link Click) [On Ad]"] <- "CPC_per_link_on_ad"
colnames(df)[colnames(df)=="CTR (All)"] <- "CTR_All"
colnames(df)[colnames(df)=="CTR (Link Click-Through Rate)"] <- "CTR_link"
colnames(df)[colnames(df)=="Cost per Purchase"] <- "cost_per_purchase"

colnames(df)[colnames(df)=="Relevance Score"] <- "relevance_score"
colnames(df)[colnames(df)=="Ad Delivery"] <- "ad_delivery"
colnames(df)[colnames(df)=="Campaign Delivery"] <- "campaign_delivery"
colnames(df)[colnames(df)=="Adds to Cart"] <- "adds_to_cart"

colnames(df)[colnames(df)=="Checkouts Initiated"] <- "checkouts_initiated"
colnames(df)[colnames(df)=="Landing Page Views"] <- "landing_page_views"
colnames(df)[colnames(df)=="Landing Page Views [On Ad]"] <- "landing_page_views_on_ad"
colnames(df)[colnames(df)=="Unique Purchases"] <- "unique_purchases"

colnames(df)[colnames(df)=="Unique Searches"] <- "unique_searches"
colnames(df)[colnames(df)=="Website Conversions"] <- "website_conversions"
colnames(df)[colnames(df)=="Website Adds to Cart"] <- "website_adds_to_cart"
colnames(df)[colnames(df)=="Website Purchases"] <- "Website_purchases"

colnames(df)[colnames(df)=="Website Searches"] <- "website_searches"
colnames(df)[colnames(df)=="Reporting Starts"] <- "reporting_starts"
colnames(df)[colnames(df)=="Reporting Ends"] <- "reporting_ends"

#new column for year and month for each campaign
df[,monthfe := month(reporting_starts)]
df[,yearfe := year(reporting_starts)]
df$yearmon <- as.yearmon(paste(df$yearfe, df$monthfe), "%Y %m")

```

2. Explore data

```{r}

names(df)

summary(df)

uniqueN( df[, .(campaign_ID, Region, monthfe, yearfe)] ) / df[, .N] #0.9974302

setkey(df, campaign_ID, Region, monthfe, yearfe)


```


Regressions

```{r}
# Detecting Multicollinearity
head(df)
df2=df[,"Reach"]
df2=df[,c("amount_spent_USD", "Reach", "Impressions", "Frequency", "link_clicks", "clicks_all", "CTR_All")]
cor(df2)
vif(df2)
# Multicollinearity testings shows that variables such as Reach, Impressions, clicks_all have Multicollinearity issue with amount_spent_USD, thus removing them from the models

df3=df[,"Reach"]
df3=df[,c("amount_spent_USD", "Frequency", "CTR_link")]
cor(df3)
vif(df3)


# Purchases as Y variable
#lm0 = lm(Purchases~amount_spent_USD+Reach+Results+clicks_all+CTR_All, data=df)

lm1 = lm(Purchases~amount_spent_USD, data=df)
lm2 = lm(Purchases~amount_spent_USD+CTR_link, data=df)

felm1 = felm(Purchases~amount_spent_USD+CTR_link | Region + yearfe + monthfe + campaign_ID, data=df)

felm2 = felm(Purchases ~ amount_spent_USD+CTR_link | Region + yearfe + monthfe + campaign_ID | 0 | Region , data=df)

felm3 = felm(Purchases ~ amount_spent_USD+CTR_link | Region + yearfe + monthfe + campaign_ID | 0 | monthfe , data=df)

felm4 = felm(Purchases ~ amount_spent_USD+CTR_link | Region + yearfe + monthfe + campaign_ID | 0 | campaign_ID , data=df)

# Heteroscedasticity tests
gqtest(lm2)
bptest(lm2)
# Both tests with p-value less than 0.05, which are significant, indicates heteroscedasticity
gqtest(felm1)
bptest(felm1)
# Both tests with p-value less than 0.05, which are significant, indicates heteroscedasticity

gqtest(felm2)
bptest(felm2)


#se increase when clustered by month. may be because there is no change in campaigns monthwise. will have to plot graph of purchases vs mnth to check if there is a trend.
#felm3 = felm(Purchases ~ Reach + amount_spent_USD + Results + clicks_all + CTR_All + monthfe | Region + monthfe | 0 | monthfe, data=df)

stargazer(lm1,lm2,felm1, felm2, felm3, felm4, title = "lm vs. felm", 
          se = list(NULL, summary(felm1, robust=TRUE)$coefficients[,2], summary(felm2, robust=TRUE)$coefficients[,2], summary(felm3, robust=TRUE)$coefficients[,2], summary(felm4, robust=TRUE)$coefficients[,2]), column.labels=c("lm1","lm2", "felm","felm clust region", "felm clust month", "felm clust campaign" ), align=TRUE, type="text")


```


Web Analytics
```{r}

#obervations by region
df[, .N, Region][order(-N)]
# of unique campaigns
df[, uniqueN(campaign_ID)]
df[, uniqueN(campaign_ID), monthfe]


#FB Ad spend and purchases by year and month
df[, .(totaladspend = sum(amount_spent_USD, na.rm = TRUE), totalpurchases=sum(Purchases, na.rm = TRUE)),by = list(yearfe, monthfe)][order(yearfe, monthfe)]

# plots of total purchases by year and month
ggplot(df, aes(x=yearmon, y=Purchases)) + geom_bar(stat="identity") + labs(title = "Total Purchases of Each Month", x = "Year-Month") + scale_x_yearmon(format="%Y/%m", n=4) + theme(axis.text.x = element_text(color="#993333", size=10, angle=45), axis.text.y = element_text(color="#993333", size=10, angle=45))

# plots of ad spend by year and month
ggplot(df, aes(x=yearmon, y=amount_spent_USD)) + geom_bar(stat="identity") + labs(title = "Monthly Spent on Ads", x = "Year-Month", y = "$ Spent") + scale_x_yearmon(format="%Y/%m", n=4) + theme(axis.text.x = element_text(color="#993333", size=10, angle=45), axis.text.y = element_text(color="#993333", size=10, angle=45))

#plot of Purchase vs amout_spent_USD
ggplot(df, aes(x=amount_spent_USD, y=Purchases)) + geom_jitter() + labs(title = "Purchases vs Ad Spend", x = "$ Ad Spend")

df_plot = subset(df, amount_spent_USD < 3000)# only keep amount_spent_USD < 3000, for better graph visualization
df_outlier = subset(df, amount_spent_USD > 3000)
ggplot(df_plot, aes(x=amount_spent_USD, y=Purchases)) + geom_jitter() + labs(title = "Purchases vs Ad Spend (Zoom In)", x = "$ Ad Spend")

#FB AD spend & Purchases for 50 US regions/states 
df[, .(totaladspend = sum(amount_spent_USD, na.rm = TRUE),totalpurchases = sum(Purchases, na.rm = TRUE)),by = list(Region)][order(-totalpurchases)][1:50] #California, Texas, Florida, New York are the TOP4 states for TotalAdSpend and TotalPurchases


#FB ad metrics by 50 US regions/states (usstatesmetrics)
usstatesmetrics = df[, .(totaladspend = sum(amount_spent_USD, na.rm = TRUE),totalpurchases = sum(Purchases, na.rm = TRUE), totalclicks = sum(link_clicks, na.rm = TRUE), conrate = sum(Purchases, na.rm = TRUE)/sum(link_clicks, na.rm = TRUE), costperpurchase = sum(amount_spent_USD, na.rm = TRUE)/sum(Purchases, na.rm = TRUE), costperclick = sum(amount_spent_USD, na.rm = TRUE)/sum(link_clicks, na.rm = TRUE) ), by = list(Region)][order(-totalpurchases)][1:50]

usstatesmetrics[order(-conrate)]
usstatesmetrics_top10conrate
usstatesmetrics[order(conrate)]
usstatesmetrics[order(-totalpurchases)]

#plot conversion rate for each states
ggplot(usstatesmetrics, aes(conrate)) + geom_freqpoly()

usstatesmetrics[order(costperpurchase)] # cost per purchase is the most important metric to company currently to measure ad campaign cost-effectiveness

usstatesmetrics[order(-costperpurchase)]

usstatesmetrics[order(costperclick)]


#FB ad metrics by AD Campaigns (campaignmetrics)
campaignmetrics = df[, .(totaladspend = sum(amount_spent_USD, na.rm = TRUE),totalpurchases = sum(Purchases, na.rm = TRUE), totalclicks = sum(link_clicks, na.rm = TRUE), conrate = sum(Purchases, na.rm = TRUE)/sum(link_clicks, na.rm = TRUE), costperpurchase = sum(amount_spent_USD, na.rm = TRUE)/sum(Purchases, na.rm = TRUE), costperclick = sum(amount_spent_USD, na.rm = TRUE)/sum(link_clicks, na.rm = TRUE) ), by = list(campaign_name)] [order(-totalpurchases)]

campaignmetrics[order(-conrate)]

campaignmetrics[order(costperpurchase)] # cost per purchase is the most important metric to company currently to measure ad campaign cost-effectiveness

campaignmetrics[order(costperclick)]

campaignmetrics[order(-totaladspend)]

campaignmetrics[order(conrate)]
campaignmetrics[order(-costperpurchase)]



#FB ad metrics by Year & Month (timemetrics)
timemetrics = df[, .(totaladspend = sum(amount_spent_USD, na.rm = TRUE),totalpurchases = sum(Purchases, na.rm = TRUE), totalclicks = sum(link_clicks, na.rm = TRUE), conrate = sum(Purchases, na.rm = TRUE)/sum(link_clicks, na.rm = TRUE), costperpurchase = sum(amount_spent_USD, na.rm = TRUE)/sum(Purchases, na.rm = TRUE), costperclick = sum(amount_spent_USD, na.rm = TRUE)/sum(link_clicks, na.rm = TRUE) ), by = list(yearfe, monthfe)][order(yearfe, monthfe)]

timemetrics

# drow plots by year-month the changes in totaladspend, total purchases, conrate change and cost per purchase change 









#amount spent vs. purchases across months for highest ad-spent region
df[Region == 'California', .(sum(amount_spent_USD, na.rm = TRUE),sum(Purchases, na.rm = TRUE)),monthfe]

#Ad spends across months for California (highest as-spent region)
plot(
  df[Region=="California", 
     sum(amount_spent_USD, na.rm = TRUE), 
     list(yearfe, monthfe)], 
  main="California", ylab="Amount spent", xlab="Month")

#Total expenditure across months
plot(
  df[, 
     sum(amount_spent_USD, na.rm = TRUE), 
     monthfe], 
  main="Total Ad Expenditure across months", ylab="Amount spent", xlab="Month")

#Total Purchases across months
plot(
  df[, 
     sum(Purchases, na.rm = TRUE), 
     monthfe], 
  main="Total Purchases across months", ylab="Purchases", xlab="Month")

#Cost per purchases across months
plot(
  df[, 
     sum(cost_per_purchase, na.rm = TRUE), 
     monthfe], 
  main="Cost Per Purchases across months", ylab="Purchases", xlab="Month")


```


